---
title: "Hw7"
author: "Cheng"
date: "6/4/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, message = FALSE, error = FALSE)
library(tidyverse)
library(dplyr); library(tidyr); library(rstan); library(ggplot2); library(ggthemes);library(gridExtra)
library(rethinking)
theme_set(theme_tufte(base_family = 'sans'))

#
library(broom)
library(loo)
```

# Question1
fit Poisson regression using `femininity` as a predictor
```{r}
# load data
data(Hurricanes)
df <- Hurricanes; remove(Hurricanes)
```

m1.1: Possion model of deaths using frmininity as a predictor
```{r}
# Setup
m1.1 <- '
  data {
    int N;
    int deaths[N];
    real fem[N];
  }

  parameters {
    real a;
    real bf;
  }
  
  model {
    vector[N] lambda;
    a   ~ normal(0,10);
    bf  ~ normal(0,10);
    for(i in 1:N) lambda[i] = a + bf * fem[i];
    deaths ~ poisson_log(lambda);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] lambda;
      for(i in 1:N) {
        lambda[i] = a + bf * fem[i];
        log_lik[i] = poisson_log_lpmf(deaths[i] | lambda[i]);
      }
    }
  }
'
```

```{r}
# Run
dat = list(
  N = nrow(df),
  deaths = df$deaths,
  fem = df$femininity
)
fit1.1 = stan(model_code = m1.1, 
              data = dat, 
              iter = 1000, 
              chains = 2, 
              cores = 2)
```

m1.2: Possion model of deaths using intercept only
```{r}
m1.2 <- '
  data {
    int N;
    int deaths[N];
  }

  parameters {
    real a;
  }
  
  model {
    vector[N] lambda;
    a   ~ normal(0,10);
    for(i in 1:N) lambda[i] = a ;
    deaths ~ poisson_log(lambda);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] lambda;
      for(i in 1:N) {
        lambda[i] = a;
        log_lik[i] = poisson_log_lpmf(deaths[i] | lambda[i]);
      }
    }
  }
'
```

```{r}
# Run
dat = list(
  N = nrow(df),
  deaths = df$deaths
)
fit1.2 = stan(model_code = m1.2, 
              data = dat, 
              iter = 1000, 
              chains = 2, 
              cores = 2)
```

Output
```{r}
print(fit1.1, include = F, pars = 'log_lik', probs = c(.1, .5, .9))
print(fit1.2, include = F, pars = 'log_lik', probs = c(.1, .5, .9))
```

Model Comparision using WAIC
```{r}

```

```{r}
fit_list <- list(fit1.1, fit1.2)
ll_list <- lapply(fit_list, extract_log_lik) 
exp_ll_list <- lapply(ll_list, exp)
rel_n_eff_list <- lapply(exp_ll_list, relative_eff, chain_id = c(rep(1, 500), rep(2, 500)))
# loo
waic_list <- list()
for(i in 1:2) {
waic_list[[i]] <- waic(ll_list[[i]], r_eff = rel_n_eff_list[[i]], cores = 4)
}
names(waic_list) <- c('fit1.1', 'fit1.2')
loo::compare(x = waic_list)
```

According to WAIC comparison model with femininity is better and take all score, but the dispersion of the difference and SE of WAIC itself is huge. The difference is less than standard error of the difference.

```{r}
post1 = as.data.frame(fit1.1)
nd <- expand.grid(fem = seq(1, 11))

# get posterior parameters of each
f_mu_2 <- function(fem) with(post1, a + bf * fem)
mu <- mapply(f_mu_2, fem = nd$fem)
mu <- exp(mu)
mu_mean <- colMeans(mu) 
mu_hpdi <- apply(mu, 2, rethinking::PI)
nd <- nd %>%
  mutate(mu = mu_mean,
  mu_hpdi_l = mu_hpdi[1,],
  mu_hpdi_h = mu_hpdi[2,])
```

Plot m1.1:
```{r}
ggplot() + 
geom_point(data = df, aes(x = df$femininity, y = df$deaths), colour = 'blue') +
geom_ribbon(data = nd, aes(x = fem, ymin = mu_hpdi_l, ymax = mu_hpdi_h), alpha = 0.4) +
geom_line(data = nd, aes(x = fem, y = mu)) +
scale_color_manual(values = "black", aesthetics = "colour") +
scale_x_continuous(breaks = seq(0, 12), limits=c(0, 12)) 
```

Intuitively there is some hidden variable that better explains deaths.Visually relation induced by the model looks suspicious for me because it looks like being caused by several outliers.


# Question2
Using gamma-Poisson model to predict deaths using femininity:
```{r}
m2.1 <- " 
data {
  int N;
  int deaths[N];
  real fem[N];
}
parameters {
  real a;
  real bf;
  real shape;
}
model {
  vector[N] mu;

  a ~ normal(0,5); 
  bf ~ normal(0,5);
  shape ~ exponential(1);
  
  for(i in 1:N) mu[i] = a + bf * fem[i];

  target += neg_binomial_2_log_lpmf( deaths | mu, shape); // use log link
}
"
```

Run
```{r}
dat = list(
  N = nrow(df),
  deaths = df$deaths,
  fem = df$femininity
)
fit2.1 = stan(model_code = m2.1, 
              data = dat, 
              iter = 1000, 
              chains = 2, 
              cores = 2)
```

```{r}
print(fit2.1)
```

Plot
```{r}
post2 = as.data.frame(fit2.1)
nd <- expand.grid(fem = seq(1, 11))

# get posterior parameters of each
f_mu_2 <- function(fem) with(post2, a + bf * fem)
mu <- mapply(f_mu_2, fem = nd$fem)
mu <- exp(mu)
mu_mean <- colMeans(mu) 
mu_hpdi <- apply(mu, 2, rethinking::PI)
nd <- nd %>%
  mutate(mu = mu_mean,
  mu_hpdi_l = mu_hpdi[1,],
  mu_hpdi_h = mu_hpdi[2,])
```

```{r}
ggplot() + 
geom_point(data = df, aes(x = df$femininity, y = df$deaths), colour = 'blue') +
geom_ribbon(data = nd, aes(x = fem, ymin = mu_hpdi_l, ymax = mu_hpdi_h), alpha = 0.4) +
geom_line(data = nd, aes(x = fem, y = mu)) +
scale_color_manual(values = "black", aesthetics = "colour") +
scale_x_continuous(breaks = seq(0, 12), limits=c(0, 12)) 
```

why the association diminished in strength?
I think this is because a much larger range of values of `(alpha, beta_femininity)` can produce, through the Gamma distribution, the same expectedvalues `lambda` via the variance in the Gamma process itself.

# Question3
Fit a series of models with varying interactions:
```{r}
# Standardize predictors
df = df %>%
    mutate(fem_std = as.vector(scale(femininity))) %>%
    mutate(min_std = as.vector(scale(min_pressure))) %>%
    mutate(dam_std = as.vector(scale(damage_norm)))
```

m3.1: No interaction: lambda ~ a + b_fem*fem_std + b_dam*dam_std + b_mp*min_std
```{r}
# Setup
m3.1 <- '
  data {
    int N;
    int deaths[N];
    real fem_std[N];
    real dam_std[N];
    real min_std[N];
  }

  parameters {
    real a;
    real b_fem;
    real b_dam;
    real b_min;
  }
  
  model {
    vector[N] lambda;
    a   ~ normal(0,5);
    b_fem  ~ normal(0,1);
    b_dam ~ normal(0,1);
    b_min ~ normal(0,1);

    for(i in 1:N) lambda[i] = a + b_fem*fem_std[i] + b_dam*dam_std[i] + b_min*min_std[i];
    deaths ~ poisson_log(lambda);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] lambda;
      for(i in 1:N) {
        lambda[i] = a + b_fem*fem_std[i] + b_dam*dam_std[i] + b_min*min_std[i];
        log_lik[i] = poisson_log_lpmf(deaths[i] | lambda[i]);
      }
    }
  }
'
```

```{r}
# Run
dat = list(
  N = nrow(df),
  deaths = df$deaths,
  fem_std = df$fem_std,
  dam_std = df$dam_std,
  min_std = df$min_std
)
fit3.1 = stan(model_code = m3.1, 
              data = dat, 
              iter = 1000, 
              chains = 2, 
              cores = 2)
```

m3.2: with interaction: b_fem_dam*fem_std[i]*dam_std[i]
```{r}
# Setup
m3.2 <- '
  data {
    int N;
    int deaths[N];
    real fem_std[N];
    real dam_std[N];
    real min_std[N];
  }

  parameters {
    real a;
    real b_fem;
    real b_dam;
    real b_min;
    real b_fem_dam;
  }
  
  model {
    vector[N] lambda;
    a   ~ normal(0,5);
    b_fem  ~ normal(0,1);
    b_dam ~ normal(0,1);
    b_min ~ normal(0,1);
    b_fem_dam ~ normal(0,1);

    for(i in 1:N) lambda[i] = a + b_fem*fem_std[i] + b_dam*dam_std[i] + b_min*min_std[i] +
    b_fem_dam*fem_std[i]*dam_std[i];
    deaths ~ poisson_log(lambda);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] lambda;
      for(i in 1:N) {
        lambda[i] = a + b_fem*fem_std[i] + b_dam*dam_std[i] + b_min*min_std[i] +
    b_fem_dam*fem_std[i]*dam_std[i];
        log_lik[i] = poisson_log_lpmf(deaths[i] | lambda[i]);
      }
    }
  }
'
```

```{r}
# Run
dat = list(
  N = nrow(df),
  deaths = df$deaths,
  fem_std = df$fem_std,
  dam_std = df$dam_std,
  min_std = df$min_std
)
fit3.2 = stan(model_code = m3.2, 
              data = dat, 
              iter = 1000, 
              chains = 2, 
              cores = 2)
```

m3.3: w/ interaction,  b_fem_min*fem_std[i]*min_std[i]
```{r}
# Setup
m3.3 <- '
  data {
    int N;
    int deaths[N];
    real fem_std[N];
    real dam_std[N];
    real min_std[N];
  }

  parameters {
    real a;
    real b_fem;
    real b_dam;
    real b_min;
    real b_fem_min;
  }
  
  model {
    vector[N] lambda;
    a   ~ normal(0,5);
    b_fem  ~ normal(0,1);
    b_dam ~ normal(0,1);
    b_min ~ normal(0,1);
    b_fem_min ~ normal(0,1);

    for(i in 1:N) lambda[i] = a + b_fem*fem_std[i] + b_dam*dam_std[i] + b_min*min_std[i] +
    b_fem_min*fem_std[i]*min_std[i];
    deaths ~ poisson_log(lambda);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] lambda;
      for(i in 1:N) {
        lambda[i] = a + b_fem*fem_std[i] + b_dam*dam_std[i] + b_min*min_std[i] +
    b_fem_min*fem_std[i]*min_std[i];
        log_lik[i] = poisson_log_lpmf(deaths[i] | lambda[i]);
      }
    }
  }
'
```

```{r}
# Run
dat = list(
  N = nrow(df),
  deaths = df$deaths,
  fem_std = df$fem_std,
  dam_std = df$dam_std,
  min_std = df$min_std
)
fit3.3 = stan(model_code = m3.3, 
              data = dat, 
              iter = 1000, 
              chains = 2, 
              cores = 2)
```

```{r}

```

m3.4: no feminiity
```{r}
# Setup
m3.4 <- '
  data {
    int N;
    int deaths[N];
    real dam_std[N];
    real min_std[N];
  }

  parameters {
    real a;
    real b_dam;
    real b_min;
  }
  
  model {
    vector[N] lambda;
    a   ~ normal(0,5);
    b_dam ~ normal(0,1);
    b_min ~ normal(0,1);

    for(i in 1:N) lambda[i] = a + b_dam*dam_std[i] + b_min*min_std[i];
    deaths ~ poisson_log(lambda);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] lambda;
      for(i in 1:N) {
        lambda[i] = a + b_dam*dam_std[i] + b_min*min_std[i];
        log_lik[i] = poisson_log_lpmf(deaths[i] | lambda[i]);
      }
    }
  }
'
```

```{r}
dat = list(
  N = nrow(df),
  deaths = df$deaths,
  dam_std = df$dam_std,
  min_std = df$min_std
)
fit3.4 = stan(model_code = m3.4, 
              data = dat, 
              iter = 1000, 
              chains = 2, 
              cores = 2)
```

Output
```{r}
print(fit3.1, include = F, pars = 'log_lik', probs = c(.1, .5, .9))
print(fit3.2, include = F, pars = 'log_lik', probs = c(.1, .5, .9))
print(fit3.3, include = F, pars = 'log_lik', probs = c(.1, .5, .9))
print(fit3.4, include = F, pars = 'log_lik', probs = c(.1, .5, .9))

```

Model comparision using WAIC
```{r}
fit_list <- list(fit3.1, fit3.2, fit3.3, fit3.4)
ll_list <- lapply(fit_list, extract_log_lik) 
exp_ll_list <- lapply(ll_list, exp)
rel_n_eff_list <- lapply(exp_ll_list, relative_eff, chain_id = c(rep(1, 500), rep(2, 500)))
# loo
waic_list <- list()
for(i in 1:4) {
waic_list[[i]] <- waic(ll_list[[i]], r_eff = rel_n_eff_list[[i]], cores = 4)
}
names(waic_list) <- c('fit3.1', 'fit3.2', 'fit3.3', 'fit3.4')
loo::compare(x = waic_list)
```

Best model according to the WAIC is m3.2 which is using damage and feminiity as interaction term.

Plot
```{r}
post3.2 = as.data.frame(fit3.2)
nd = expand.grid(fem_std = seq(-2,2,length.out = 10)) %>%
  mutate(dam_std = seq(-1,5,length.out = 10)) %>%
  mutate(min_std = seq(-2,1,length.out = 10))

# get posterior parameters of each
f_mu_2 <- function(fem_std, dam_std, min_std) with(post3.2, a + b_fem*fem_std + b_dam*dam_std + b_min*min_std + b_fem_dam*fem_std*dam_std)
mu <- mapply(f_mu_2, fem_std = nd$fem_std, dam_std = nd$dam_std, min_std = nd$min_std)
mu <- exp(mu)
mu_mean <- colMeans(mu) 
mu_hpdi <- apply(mu, 2, rethinking::PI)
nd <- nd %>%
  mutate(mu = mu_mean,
  mu_hpdi_l = mu_hpdi[1,],
  mu_hpdi_h = mu_hpdi[2,])
```

```{r}
ggplot() + 
geom_point(data = df, aes(x = df$fem_std, y = df$deaths), colour = 'blue') +
geom_ribbon(data = nd, aes(x = fem_std, ymin = mu_hpdi_l, ymax = mu_hpdi_h), alpha = 0.4) +
geom_line(data = nd, aes(x = fem_std, y = mu)) +
scale_color_manual(values = "black", aesthetics = "colour") 
```

# Question 4
```{r}
df$log_dam_std <- as.vector(scale(log(df$damage_norm)))
```

m4.1: Try 
```{r}
# Setup
m4.1 <- '
  data {
    int N;
    int deaths[N];
    real fem_std[N];
    real log_dam_std[N];
    real min_std[N];
  }

  parameters {
    real a;
    real b_fem;
    real b_ldam;
    real b_min;
  }
  
  model {
    vector[N] lambda;
    a   ~ normal(0,5);
    b_fem  ~ normal(0,1);
    b_ldam ~ normal(0,1);
    b_min ~ normal(0,1);

    for(i in 1:N) lambda[i] = a + b_fem*fem_std[i] + b_ldam* log_dam_std[i] + b_min*min_std[i];
    deaths ~ poisson_log(lambda);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] lambda;
      for(i in 1:N) {
        lambda[i] = a + b_fem*fem_std[i] + b_ldam*log_dam_std[i] + b_min*min_std[i];
        log_lik[i] = poisson_log_lpmf(deaths[i] | lambda[i]);
      }
    }
  }
'
```

Run log(damage_norm)
```{r}
# Run
dat = list(
  N = nrow(df),
  deaths = df$deaths,
  fem_std = df$femininity,
  log_dam_std = df$log_dam_std,
  min_std = df$min_std
)
fit4.1 = stan(model_code = m4.1, 
              data = dat, 
              iter = 1000, 
              chains = 2, 
              cores = 2)
```

m4.2: the setting is same as 3.1 but using log(damage_norm)
```{r}
# Setup
m4.2 <- '
  data {
    int N;
    int deaths[N];
    real fem_std[N];
    real log_dam_std[N];
  }

  parameters {
    real a;
    real b_fem;
    real b_ldam;
    real b_fem_ldam;
  }
  
  model {
    vector[N] lambda;
    a   ~ normal(0,5);
    b_fem  ~ normal(0,1);
    b_ldam ~ normal(0,1);
    b_fem_ldam ~ normal(0,1);

    for(i in 1:N) lambda[i] = a + b_fem*fem_std[i] + b_ldam*log_dam_std[i]  +
    b_fem_ldam*fem_std[i]*log_dam_std[i];
    deaths ~ poisson_log(lambda);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] lambda;
      for(i in 1:N) {
        lambda[i] = a + b_fem*fem_std[i] + b_ldam*log_dam_std[i]  +
    b_fem_ldam*fem_std[i]*log_dam_std[i];
        log_lik[i] = poisson_log_lpmf(deaths[i] | lambda[i]);
      }
    }
  }
'
```

```{r}
# Run
dat = list(
  N = nrow(df),
  deaths = df$deaths,
  fem_std = df$fem_std,
  log_dam_std = df$log_dam_std
)
fit4.2 = stan(model_code = m4.2, 
              data = dat, 
              iter = 1000, 
              chains = 2, 
              cores = 2)
```

Output
```{r}
print(fit4.1, include = F, pars = 'log_lik', probs = c(.1, .5, .9))
print(fit4.2, include = F, pars = 'log_lik', probs = c(.1, .5, .9))

```

Model Comparsion musing WAIC
```{r}
fit_list <- list(fit4.1, fit4.2, fit3.1, fit3.2)
ll_list <- lapply(fit_list, extract_log_lik) 
exp_ll_list <- lapply(ll_list, exp)
rel_n_eff_list <- lapply(exp_ll_list, relative_eff, chain_id = c(rep(1, 500), rep(2, 500)))
# loo
waic_list <- list()
for(i in 1:4) {
waic_list[[i]] <- waic(ll_list[[i]], r_eff = rel_n_eff_list[[i]], cores = 4)
}
names(waic_list) <- c('fit4.1', 'fit4.2', 'fit3.1', 'fit3.2')
loo::compare(x = waic_list)
```
Model 4.2 performs is the best model in this case.

Plot
```{r}
post3.2 = as.data.frame(fit3.2)
nd = expand.grid(fem_std = seq(-2,2,length.out = 10)) %>%
  mutate(log_dam_std = seq(-3,2,length.out = 10)) %>%
  mutate(min_std = seq(-2,1,length.out = 10))

# get posterior parameters of each
f_mu_2 <- function(fem_std, dam_std, min_std) with(post3.2, a + b_fem*fem_std + b_dam*dam_std + b_min*min_std + b_fem_dam*fem_std*dam_std)
mu <- mapply(f_mu_2, fem_std = nd$fem_std, dam_std = nd$log_dam_std, min_std = nd$min_std)
mu <- exp(mu)
mu_mean <- colMeans(mu) 
mu_hpdi <- apply(mu, 2, rethinking::PI)
nd <- nd %>%
  mutate(mu = mu_mean,
  mu_hpdi_l = mu_hpdi[1,],
  mu_hpdi_h = mu_hpdi[2,])
```

```{r}
df.male <- filter(df, female!=1)
df.female <- filter(df, female==1)
ggplot() + 
  geom_point(data = df.male , aes(x = log_dam_std, y = deaths), color = 'blue') +
  geom_point(data = df.female , aes(x = log_dam_std, y = deaths), color = 'red') +
  geom_ribbon(data = nd, aes(x = log_dam_std, ymin = mu_hpdi_l, ymax = mu_hpdi_h), alpha = 0.4) +
  geom_line(data = nd, aes(x = log_dam_std, y = mu)) +
  scale_color_manual(values = "black", aesthetics = "colour") 
  
  
```

With log scale of damage there is no need for min_pressure variable.Model becomes more accurate in predictions. According to coefficients it's only interaction of femininicity and log(damage_norm) that really matters.

# Question 5

Load data
```{r}
data("bangladesh")
d <- bangladesh
```

Data pre-processing
```{r}
d$district_id <- as.integer(as.factor(d$district))
d$use_contraception <- d$use.contraception
d$age_centered <- d$age.centered
d$living_children <- d$living.children
d <- select(d,-use.contraception, -age.centered, -district, -living.children)
```

m5.1: fixed effect model using dummy variables for district
```{r}
m5.1='
  data {
    int N;
    int K;  // number of clusters
    int dis_id[N];
    int use_con[N];
  }
  parameters {
    vector[K] a_dis;
  }
  model {
    vector[N] p;
    target += normal_lpdf(a_dis | 0, 5);

    for (i in 1:N) p[i] = inv_logit( a_dis[dis_id[i]]);   
    target += binomial_lpmf(use_con | 1, p);
  }
  generated quantities {
    vector[N] log_lik;
    {
    vector[N] p;
    for(i in 1:N) {
      p[i] = inv_logit( a_dis[dis_id[i]] );
      log_lik[i] = binomial_lpmf(use_con[i] | 1, p[i]);
    }
    }
  }'
```

Run the model
```{r}
dat <- list(
  N = nrow(d),
  use_con = d$use_contraception,
  K = max(d$district_id),
  dis_id = d$district_id
)
fit5.1 <- stan(model_code = m5.1, data = dat, iter = 1000, chains = 2, cores = 2)
```

m5.2: multilevel model with varing intercepts for district
```{r}
m5.2='
  data {
    int N;
    int K;  // number of clusters
    int dis_id[N];
    int use_con[N];
  }
  parameters {
    vector[K] a_dis;
    real alpha;
    real <lower=0> sigma;
  }
  model {
    vector[N] p;
    target += normal_lpdf(alpha | 0, 1);
    target += cauchy_lpdf(sigma | 0, 1);
    target += normal_lpdf(a_dis | alpha, sigma);

    for (i in 1:N) p[i] = inv_logit( a_dis[dis_id[i]]);   
    target += binomial_lpmf(use_con | 1, p);
  }
  generated quantities {
    vector[N] log_lik;
    {
    vector[N] p;
    for(i in 1:N) {
      p[i] = inv_logit( a_dis[dis_id[i]] );
      log_lik[i] = binomial_lpmf(use_con[i] | 1, p[i]);
    }
    }
  }'
```

```{r}
dat <- list(
  N = nrow(d),
  use_con = d$use_contraception,
  K = max(d$district_id),
  dis_id = d$district_id
)
fit5.2 <- stan(model_code = m5.2, data = dat, iter = 1000, chains = 2, cores = 2)
```

Output
```{r}
print(fit5.1, include = F, pars = 'log_lik', probs = c(.1, .5, .9))
print(fit5.2, include = F, pars = 'log_lik', probs = c(.1, .5, .9))
```

Model Comparision using WAIC
```{r}
library(loo)
ll12_1 <- extract_log_lik(fit5.1)
ll12_2 <- extract_log_lik(fit5.2)
reff1 <- relative_eff(ll12_1, chain_id = c(rep(1, 500), rep(2, 500)), cores =2)
reff2 <- relative_eff(ll12_2, chain_id = c(rep(1, 500), rep(2, 500)), cores =2)
waic5.1 <- waic(ll12_1, r_eff = reff1, cores = 2)
waic5.2 <- waic(ll12_2, r_eff = reff2, cores = 2)
loo::compare(waic5.1, waic5.2)
c(waic5.1$waic,waic5.2$waic)
```

Multilevel model performs better.

Plot
```{r}
d.res <- d %>% 
  group_by(district_id) %>% 
  summarise(
    cnt=n(), 
    ttl_use_c=sum(use_contraception),
    rate=ttl_use_c/cnt
  ) %>% 
  as.data.frame() %>%
  mutate(
    d_label = reorder(as.factor(paste0(district_id,'/n=',cnt)), cnt)
  ) %>% 
  arrange(district_id)
```


```{r}
post5.2 <- as.data.frame(fit5.2, pars = c('alpha', 'sigma', 'a_dis'))
post5.1 <- as.data.frame(fit5.1, pars = c('a_dis'))
d.res$pred5.1 <- post5.1 %>% colMeans %>% plogis
d.res$pred5.2 <- post5.2[,-c(1:2)] %>% colMeans %>% plogis

ggplot(d.res) + 
  geom_vline(xintercept = c(20, 40)) +
  geom_hline(yintercept = plogis(mean(post5.2$alpha)), linetype = 'dashed') +
  geom_point(aes(x = district_id, y = rate), colour = 'dodgerblue') +
  geom_point(aes(x = district_id, y = pred5.1), shape = 21, colour = 'green') +
  geom_point(aes(x = district_id, y = pred5.2), shape = 21, colour = 'red') +
  scale_x_continuous(limits = c(0, 60), breaks = c(1, 20, 40, 60)) +
  labs(x = 'district_id', y = 'rate') 
```

blue: actual data
green: pooled model
red: fixed model

