---
title: "Assignment-5"
author: "Cheng"
date: "5/14/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, message = FALSE, error = FALSE)
library(tidyverse)
library(dplyr); library(tidyr); library(rstan); library(ggplot2); library(ggthemes);library(gridExtra)
theme_set(theme_tufte(base_family = 'sans'))
library(rethinking)

#
library(broom)
library(loo)
library(GGally) 
```

# Question1

## (a) Fit the model using rstan. Is the quadratic approximation okay?
```{r}
# load the data
library(MASS)
data(eagles)
dd <- eagles
str(dd)

# transform data
dd$pirate <- ifelse(dd$P == "L", 1, 0)
dd$adult <- ifelse(dd$A == "A", 1, 0)
dd$victim <- ifelse(dd$V == "L", 1, 0)
```

Train the model using Rstan
```{r}
# Rstan setup
m1='
  data {
    int N;
    int<lower=0, upper=1> pirate[N];
    int<lower=0, upper=1> adult[N];
    int<lower=0, upper=1> victim[N];
    int N_y[N];                       // number of successful applicants
    int N_n[N];                       // total number of attempts
  }

  parameters {
    real a;
    real bp;
    real bv;
    real ba;
  }

  model {
    vector[N] p;
    a  ~ normal(0,10);
    bp ~ normal(0,5);
    bv ~ normal(0,5);
    ba ~ normal(0,5);
  
    for (i in 1:N){
      p[i] = inv_logit(a + bp * pirate[i] + ba * adult[i] + bv * victim[i]);
    }

    N_y ~ binomial(N_n, p);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] p_y;
      for(n in 1:N) {
        p_y[n] = a + bp * pirate[n] + ba * adult[n] + bv * victim[n];
        log_lik[n] = binomial_logit_lpmf(N_y[n] | N_n[n], p_y[n]);
      }
    }
  }
'

dat <- list(
  N = NROW(dd),
  N_n = dd$n,
  N_y = dd$y,
  pirate = dd$pirate,
  adult = dd$adult,
  victim = dd$victim
)

fit1<- stan(model_code = m1, 
                data = dat, 
                iter = 1000, 
                chains = 2, 
                cores = 2)
```

Train the model using map() to see how quadratic approximation works
```{r}
m1_qr <- map(
  alist(
    y ~ dbinom( n, p),
    logit(p) <- a + bp*pirate + ba*adult + bv*victim,
    a ~ dnorm(0, 10),
    c(bp, ba, bv) ~ dnorm(0, 5)),
  data=dd
)
```

Compare the result of MCMC and quadratic approximation
```{r}
# Rstan using MCMC
print(fit1)
# quadratic approximation
precis(m1_qr)
```

```{r}
# "select()" i'm not sure why rmd would have error, it's ok when I run R file.... so i would like to skip this part and intepret the result from previors result
# Comparing estimates
# coef <-
#   select(tidy(fit1)[1:4,], term, estimate)  %>%
#   rename(., MCMC = estimate) %>%
#   mutate(MCMC = round(MCMC, digits = 2)) %>%
#   mutate(quadratic = c(0.59, 4.24, -4.59, 1.08))
# 
# print(coef)
```

As we can see from the table, there is a slight difference of estimates when using MCMC(rstan) and quadratic approximation(map), especially for the parameter bv and bp.

Following I would use the output from Rstan to intepret the results.

## (b) Now interpret the estimates.
```{r}
post1 <- as.data.frame(fit1)
print(mean(logistic(post1$a)))
```

The intercept is at 0.69, meaning that if all other predictor variables are 0, then the probability of a successful attempt is 0.6433955

```{r}
print(mean(logistic(post1$a + post1$bp)))
print(mean(logistic(post1$a + post1$ba)))
print(mean(logistic(post1$a + post1$bv)))

```
If the pirating eagle is large, then this probability increases to almost 100%
If the pirating eagle is an adult, the probability of a successful attempt is quite high with a mean of about 84%. 
If the victim eagle is large, then it also doesn't improve the chances much when the pirating eagle is an adult. While higher than before, it is still mostly below 10%.

### (1)
```{r}
# create label
lab <- c()
for(i in c(1:nrow(dd))){
  tmp <- c(paste(dd$pirate[i], dd$adult[i], dd$victim[i], sep="/"))
  lab <- c(lab, tmp)
}

dd <-
  dd %>%
  mutate(case = factor(1:nrow(dd))) %>%
  mutate(label = lab)
```

plot the Predicted Probability of Success
```{r}
post1 <- as.data.frame(fit1)
f_mu <- function(p, v, a) plogis(post1$a + post1$bp * p + post1$bv * v + post1$ba * a)
p_y_hat <- mapply(f_mu, p = (dd$pirate == 1), v = (dd$victim == 1), a = (dd$adult == 1) )

# get expectation and 89% intervals of the expectation
dd <- 
  dd %>%
  mutate(p_y = y / n,
         p_hat_mean = colMeans(p_y_hat),
         p_hat_hpdi_l = apply(p_y_hat, 2, rethinking::HPDI)[1,], # 2: by row
         p_hat_hpdi_h = apply(p_y_hat, 2, rethinking::HPDI)[2,])

# plot 
ggplot(dd) + 
  geom_point(aes(x = label, y = p_y), color = 'dodgerblue') + 
  geom_segment(aes(x = label, xend = label, y = p_hat_hpdi_l, yend = p_hat_hpdi_h)) + 
  geom_point(aes(x = label, y = p_hat_mean), shape = 21, fill = 'white') + 
  scale_y_continuous(limits = c(0, 1)) +
  theme(panel.border = element_rect(colour = "gray90", fill=NA, size=1),
        panel.spacing.x = unit(-0.5, "mm"),
        panel.spacing.y = unit(2, "lines")) + 
  labs(x = 'Pirate/ Adult/ Victim', y = 'Predicted Probability of Success')

```
Blue filled points show the observed proportions whereas the estimates probability and 89% percent interval are shown in black and open points. Except for the case 0/0/0 (small, immature pirate and small victim), all observed proportions of success are within the 89% interval for the predicted probabilities.


### (2)
plot the Predicted Success Count
```{r}
f_mu <- function(n, p, v, a) n * plogis(post1$a + post1$bp * p + post1$bv * v + post1$ba * a)
y_hat <- mapply(f_mu, n = dd$n, p = (dd$pirate == 1), v = (dd$victim == 1), a = (dd$adult == 1) )

# how to choose the size?
# f_mu <- function(p, v, a) rbinom(n = 1e3, size = 20, prob = plogis(post1$a + post1$bp * p + post1$bv * v + post1$ba * a ))
# y_hat <- mapply(f_mu, p = (dd$pirate == 1), v = (dd$victim == 1), a = (dd$adult == 1))

dd <- 
  dd %>%
  mutate(y_hat_mean = colMeans(y_hat),
         y_hat_hpdi_l = apply(y_hat, 2, rethinking::HPDI)[1,], # 2: by row
         y_hat_hpdi_h = apply(y_hat, 2, rethinking::HPDI)[2,])

# plot
ggplot(dd) + 
  geom_point(aes(x = label, y = y), color = 'dodgerblue') + 
  geom_segment(aes(x = label, xend = label, y = y_hat_hpdi_l, yend = y_hat_hpdi_h)) + 
  geom_point(aes(x = label, y = y_hat_mean), shape = 21, fill = 'white') + 
  theme(panel.border = element_rect(colour = "gray90", fill=NA, size=1),
        panel.spacing.x = unit(-0.5, "mm"),
        panel.spacing.y = unit(2, "lines")) + 
  labs(x = 'Pirate/ Adult/ Victim', y = 'Predicted Count of Success')

```
Even though the predicted probability interval for the base case 0/0/0 did not contain the observed proportions of success, the observed number of successful attempts is contained in its 89% interval for the predicted success count.

## (c) Now try to improve the model. Consider an interaction between the pirate’s size and age (immature or adult). Compare this model to the previous one, using WAIC to interpret.

```{r}
# Rstan setup: add interaction term
m2='
  data {
    int N;
    int<lower=0, upper=1> pirate[N];
    int<lower=0, upper=1> adult[N];
    int<lower=0, upper=1> victim[N];
    int N_y[N];                       // number of successful applicants
    int N_n[N];                       // total number of attempts
  }

  parameters {
    real a;
    real bp;
    real bv;
    real ba;
    real bap;
  }

  model {
    vector[N] p;
    a  ~ normal(0,10);
    bp ~ normal(0,5);
    bv ~ normal(0,5);
    ba ~ normal(0,5);
    bap ~ normal(0,5);
  
    for (i in 1:N){
      p[i] = inv_logit(a + bp * pirate[i] + ba * adult[i] + bv * victim[i] + bap * adult[i] * pirate[i]);
    }

    N_y ~ binomial(N_n, p);
  }

  generated quantities {
    vector[N] log_lik;
    {
      vector[N] p_y;
      for(n in 1:N) {
        p_y[n] = a + bp * pirate[n] + ba * adult[n] + bv * victim[n] + bap * adult[n] * pirate[n];
        log_lik[n] = binomial_logit_lpmf(N_y[n] | N_n[n], p_y[n]);
      }
    }
  }
'

dat <- list(
  N = NROW(dd),
  N_n = dd$n,
  N_y = dd$y,
  pirate = dd$pirate,
  adult = dd$adult,
  victim = dd$victim
)

fit2<- stan(model_code = m2, 
                data = dat, 
                iter = 1000, 
                chains = 2, 
                cores = 2)

m3='
data {
int N;
int N_y[N];                       // number of successful applicants
int N_n[N];                       // total number of attempts
}

parameters {
real a;

}

model {
vector[N] p;
a  ~ normal(0,10);


for (i in 1:N){
p[i] = inv_logit(a);
}

N_y ~ binomial(N_n, p);
}

generated quantities {
vector[N] log_lik;
{
  vector[N] p_y;
  for(n in 1:N) {
  p_y[n] = a ;
  log_lik[n] = binomial_logit_lpmf(N_y[n] | N_n[n], p_y[n]);
  }
}
}
'

dat <- list(
  N = NROW(dd),
  N_n = dd$n,
  N_y = dd$y
)

fit3<- stan(model_code = m3, 
            data = dat, 
            iter = 1000, 
            chains = 2, 
            cores = 2)
```

### Review correlations among posterior of parameters using improved model
```{r}
#library(GGally) 
post2 <- as.data.frame(fit2)
post2[,1:5] %>%
  ggpairs() + theme_tufte(base_family = 'sans')

```

As before, we have some correlations between the coefficients: bap and ba, as well as bap and bp are negatively correlated. bp and baare now positively correlated and bp and bv are again negatively correlated but slightly less than in the model without interaction.

### Comparing WAIC
```{r}
# initial model
log_lik_m1 <- extract_log_lik(fit1, merge_chains = FALSE)
r_eff <- relative_eff(exp(log_lik_m1))
loo_m1 <- loo(log_lik_m1, r_eff = r_eff, cores = 2)
waic1 <- loo(log_lik_m1)

# include interaction term
log_lik_m2 <- extract_log_lik(fit2, merge_chains = FALSE)
r_eff <- relative_eff(exp(log_lik_m2))
loo_m2 <- loo(log_lik_m2, r_eff = r_eff, cores = 2)
waic2 <- loo(log_lik_m2)

# only include intercept
log_lik_m3 <- extract_log_lik(fit3, merge_chains = FALSE)
r_eff <- relative_eff(exp(log_lik_m3))
loo_m2 <- loo(log_lik_m3, r_eff = r_eff, cores = 2)
waic3 <- loo(log_lik_m3)

loo::compare(waic1, waic2, waic3)
```

I compared 3 models: initial model, the model with interaction term and the model only included intercep. As we can see from the table, the model with interaction term got the best performance in this case.